MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-14 docs/paper/out/paper.tex
correct wording in Results/Scala -- paper
it was basically unreadable, a bit better now

In this section we describe the resources and Scala libraries developed
by the authors on top of which MG7 is built.

\href{http://www.scala-lang.org/}{Scala}, a hybrid object-functional
programming language, was chosen based on the possibility of using
certain advanced programming styles, and Java interoperability, which
let us build on the vast number of existing Java libraries; we take
advantage of this when using Bio4j as an API for the NCBI taxonomy. It
has support for type-level programming, type-dependent types (through
type members) and singleton types, which permits a restricted form of
dependent types where types can depend essentially on values determined
at compile time (through their corresponding singleton types).
Conversely, through implicits one can retrieve the value corresponding
to a singleton type.

>>>>

In this section we describe the resources and libraries developed by the
authors on top of which MG7 is built. All MG7 code is written in
\href{http://www.scala-lang.org/}{Scala}, a hybrid object-functional
programming language. Scala was chosen based on the possibility of using
certain advanced programming styles, and Java interoperability, which
let us build on the vast number of existing Java libraries; we take
advantage of this when using Bio4j as an API for the NCBI taxonomy. It
has support for type-level programming, type-dependent types (through
type members) and singleton types, which permits a restricted form of
dependent types where types can depend essentially on values determined
at compile time (through their corresponding singleton types).
Conversely, through implicits one can retrieve the value corresponding
to a singleton type.
